SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-03-06 scipy-1.0/paper.tex
capitalized Astropy

SciPy adopted an official Governance Document on August 3, 2017\cite{SciPyProjectGovernance}. A Steering Council, currently composed of 18 members, oversees daily development of the project by contributing code and reviewing contributions from the community. Council Members have commit rights to the project repository, but they are expected to merge changes only when there are no substantive community objections. The Chair of the Steering Council, Ralf Gommers, is responsible for initiating biannual technical reviews of project direction and summarizing any private Council activities to the broader community. The project's Benevolent Dictator for Life (BDFL), Pauli Virtanen, has overruling authority on any matter, but the BDFL is expected to act in good faith and only exercise this authority when the Steering Council cannot reach agreement.

SciPy's official Code of Conduct was approved on October 24, 2017. In summary, there are five Specific Guidelines:
\emph{be open} to everyone participating in our community;
\emph{be empathetic and patient} in resolving conflicts;
\emph{be collaborative}, as we depend on each other to build the library;
\emph{be inquisitive}, as early identification of issues can prevent serious consequences; and
\emph{be careful with wording}.
The Code of Conduct specifies how breaches can be reported to a Code of Conduct Committee, and outlines procedures for the Committee's response. Our Diversity Statement ``welcomes and encourages participation by everyone''.

@@

The scientific Python ecosystem includes many examples
of domain-specific software libraries building on top
of SciPy features, and then returning to the base SciPy library
to suggest and even implement improvements to enable
more effective science applications. For example, there
are common contributors to the SciPy and astropy core
libraries\cite{astropy-2018}, and what works well for 
one of the code bases, infrastructures, or communities 
is often transferred in some form to the other. At the code
base level, the \texttt{binned\_statistic} functionality
is one such cross-project contribution---it was initially
developed in an Astropy-affiliated package
and then placed in SciPy after the fact.

>>>>

SciPy adopted an official Governance Document on August 3,
2017\cite{SciPyProjectGovernance}.  We have a Benevolent Dictator for Life
(BDFL), Pauli Virtanen, leading the project, following a detailed discussion of
the governance model with the community on the mailing list.  In practice, the
overruling authority of the BDFL is anticipated to be used only when the
Steering Council cannot agree on a matter.  The BDFL is expected to consider
any strong indications that they should step down; although the BDFL may
appoint a successor, it is generally expected that the Steering Council will be
consulted on the matter.

The (currently) 18 member Steering Council is chaired by Ralf Gommers and
performs a number of tasks including nominating and voting on new Council
Members and actively contributing to the progress of the project (could be
code review but also outreach activities, etc.). Generally, one year of sustained
and substantial contributions (not restricted to source code contributions)
that improve the project are the prerequisites for nomination of new Council
Members. Council Members do not get special treatment for the vast majority of
the day to day project activities (code submission / review), though it is
anticipated that their experience with the project will serve as helpful
guidance in many matters.  Council Members have commit rights to the project,
but will typically only incorporate changes when there are no substantive
community objections. The Chair of the Steering Council is responsible for
starting more formal technical reviews of the direction of the project,
ensuring that the composition of the Council remains current, and communicating
/ summarizing any Council activities performed privately to the broader
community. We also describe in some detail how institutional partners may
contribute to the project, but no financial weight from grants or other sources
may be leveraged to circumvent or overrule the technical direction of the
project decided upon by the Steering Committee. The Chair does not have a fixed
term but is nominated by the Steering Committee and is expected to yield to
substantive claims that stepping down is the appropriate action.

SciPy adopted an official Code of Conduct on October 24, 2017
\cite{SciPyCodeOfConduct}, drawing inspiration from the Apache Foundation Code
of Conduct\cite{ApacheCodeOfConduct}, the Contributor Covenant
\cite{ContributorConvenant}, the Jupyter Code of Conduct \cite{Jupyter_COC},
and the Open Source Guides - Code of Conduct\cite{OSG_COC}. In short, we stated
five specific guidelines: \emph{be open} (to anyone participating in our
community), \emph{be empathetic and patient} (in resolving conflicts), \emph{be
collaborative} (we depend on each other to build up the tools in the library),
\emph{be inquisitive} (identifying issues early on can be helpful to everyone),
and \emph{be careful with wording} (do not harass or exclude).  We outlined a
broad diversity inclusion statement, and provide instructions for contacting
the three members of our Code of Conduct Committee or an external
representative on the NumFOCUS Board of Directors.

@@

The scientific Python ecosystem includes many examples
of domain-specific software libraries building on top
of SciPy features, and then returning to the base SciPy library
to suggest and even implement improvements to enable
more effective science applications. For example, there
are common contributors to the SciPy and Astropy core
libraries\cite{astropy-2018}, and what works well for 
one of the code bases, infrastructures, or communities 
is often transferred in some form to the other. At the code
base level, the \texttt{binned\_statistic} functionality
is one such cross-project contribution---it was initially
developed in an Astropy-affiliated package
and then placed in SciPy after the fact.
